\documentclass[a4paper,10.5pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{geometry}
\usepackage{xcolor}

\geometry{top=0.40in, bottom=0.40in, left=0.50in, right=0.50in}

\definecolor{accent}{RGB}{20,40,100}
\definecolor{linkblue}{RGB}{0,70,180}
\definecolor{ruleblue}{RGB}{37,99,235}

\hypersetup{
  colorlinks=true,
  urlcolor=linkblue,
  linkcolor=linkblue
}

\setlength{\parindent}{0pt}
\pagestyle{empty}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\color{ruleblue}\titlerule]
\titlespacing*{\section}{0pt}{7pt}{4pt}

\setlist[itemize]{noitemsep, topsep=1pt, leftmargin=*, label=\textbullet}

\newcommand{\resumeSubheading}[4]{%
  \noindent\textbf{\color{accent}#1} \hfill \textbf{\small#2} \\
  \noindent\textit{\small\color{gray}#3} \hfill \textit{\small\color{gray}#4} \vspace{2pt}%
}

\newcommand{\resumeItem}[1]{\item\small #1}

\begin{document}

%================ HEADER ================
\begin{center}
  {\fontsize{22}{26}\selectfont \textbf{\color{accent}Ishita Singh}}\\[3pt]
  {\small Software Engineer \,\textbar\, Full-Stack \& Distributed Systems \,\textbar\, Applied AI}\\[5pt]
  {\small
    +91-9817409208
    \,\textbar\,
    \href{mailto:singhish0304@gmail.com}{singhish0304@gmail.com}
    \,\textbar\,
    \href{https://linkedin.com/in/ishita-singh-7b98752aa}{LinkedIn}
    \,\textbar\,
    \href{https://github.com/Ishita-coder27}{GitHub}
    \,\textbar\,
    \href{https://portfolioo-jade-iota.vercel.app/}{Portfolio}
    \,\textbar\,
    Noida, India
  }
\end{center}

\vspace{2pt}

%================ SUMMARY ================
\section*{Professional Summary}

Pre-final year CSE student and full-stack software engineer with \textbf{3 internships and 5+ production projects} spanning real-time distributed systems, scalable web applications, and applied AI. Strong CS fundamentals --- \textbf{500+ DSA problems solved} with solid grounding in Data Structures, Algorithms, OOP, Operating Systems, DBMS, and Computer Networks. Proficient in \textbf{C++, Python, JavaScript, and SQL}. Selected for \textbf{Amazon ML Summer School 2025}. Passionate about building reliable, scalable, well-engineered software and learning new technologies quickly.

%================ TECHNICAL SKILLS ================
\section*{Technical Skills}

\begin{tabular}{@{}p{0.20\linewidth} p{0.77\linewidth}@{}}
\textbf{Languages:}        & C++, Python, JavaScript, SQL, Dart \\[2pt]
\textbf{CS Fundamentals:}  & Data Structures \& Algorithms, OOP, Operating Systems, DBMS, Computer Networks, System Design \\[2pt]
\textbf{Backend:}          & Node.js, Express.js, FastAPI, REST APIs, WebSockets, WebRTC, Socket.IO, JWT Auth \\[2pt]
\textbf{Frontend:}         & React, Vite, Tailwind CSS, HTML/CSS \\[2pt]
\textbf{Databases:}        & MongoDB, MySQL, PostgreSQL, Redis \\[2pt]
\textbf{Systems Concepts:} & Distributed Systems, Concurrency, Caching, Load Balancing, Real-Time Communication \\[2pt]
\textbf{Tools / DevOps:}   & Git \& GitHub, GitHub Actions, Docker, Linux, Postman, Vercel \\[2pt]
\textbf{Applied AI:}       & LLM Integration, RAG, Prompt Engineering, Vector Databases, NLP (Python) \\
\end{tabular}

%================ EXPERIENCE ================
\section*{Professional Experience}

\resumeSubheading
{Software Engineer Intern --- ISRPL \,\href{https://drive.google.com/file/d/18-IPNTV7WDPqWt1JuZBNGiwhsbWZ6-QL/view?usp=sharing}{\small[Certificate]}}{May 2025 -- Jul 2025}
{Information Technology Department}{Noida, India}
\begin{itemize}
  \resumeItem{Architected and delivered a \textbf{Near Miss Reporting \& Investigation Management Web App} end-to-end, with \textbf{multi-role RBAC} across 5 roles (Initiator, HOD, Concerned Manager, Executor Manager, HSE Team).}
  \resumeItem{Built backend \textbf{REST APIs} with role-gated endpoints, data-validation layers, and \textbf{SQL-based reporting pipelines}; designed normalized relational schemas for audit trails and compliance exports.}
  \resumeItem{Developed interactive \textbf{dashboards and real-time investigation tracking} with automated status updates; reduced manual closure time by $\sim$\textbf{35\%}.}
\end{itemize}

\vspace{4pt}

\resumeSubheading
{Software Engineer Intern --- Arresto Solutions Pvt. Ltd.}{Apr 2026 -- Jun 2026}
{Safety-Tech SaaS Startup \,|\, Remote}{Noida, India}
\begin{itemize}
  \resumeItem{Engineered backend services with \textbf{FastAPI (Python)} and a cross-platform \textbf{Flutter} frontend for an AI-powered LMS, exposing clean, well-structured REST APIs for real-time content generation.}
  \resumeItem{Built a document-processing pipeline using \textbf{text extraction, embeddings, and a vector database} to automatically generate structured course content from raw source material.}
  \resumeItem{Supported end-to-end testing, validation, and deployment of production modules used across enterprise clients; reduced manual content-authoring effort by $\sim$\textbf{40\%}.}
\end{itemize}

\vspace{4pt}

\resumeSubheading
{Web Development Intern --- EHS Safety Club \,\href{https://drive.google.com/file/d/1Qdter8Ndw98bpQBjL-DrfLcrUbw5Wf1_/view?usp=sharing}{\small[Certificate]}}{May 2024 -- Aug 2024}
{Remote}{}
\begin{itemize}
  \resumeItem{Engineered reusable UI components and REST API integrations; reduced frontend load time by $\sim$\textbf{25\%} and shipped production-level features in an agile team.}
\end{itemize}

%================ PROJECTS ================
\section*{Projects}

%--- CodeVanta
\noindent\textbf{\color{accent}CodeVanta --- Real-Time Collaborative Coding Platform}
\hfill \emph{React.js, Node.js, MongoDB, Socket.IO, WebRTC}\\
{\small
  \href{https://github.com/Ishita-coder27/Codevanta}{GitHub}
  \,\textbar\,
  \href{https://codevanta-orcin.vercel.app/}{Live Demo}
}
\begin{itemize}
  \resumeItem{Engineered a real-time collaborative coding platform with a \textbf{shared Monaco editor} and \textbf{live WebSocket synchronization}, handling concurrent multi-user edits with low-latency state sync.}
  \resumeItem{Integrated \textbf{WebRTC peer-to-peer video}, a DSA problem bank, and session history for pair programming --- a strong exercise in real-time networking and concurrency.}
\end{itemize}

\vspace{4pt}

%--- VOCA AI
\noindent\textbf{\color{accent}VOCA AI --- Mock Interview Platform}
\hfill \emph{React, Node.js, Express.js, MongoDB, Voice AI}\\
{\small
  \href{https://github.com/Ishita-coder27/ai-interviewer}{GitHub}
  \,\textbar\,
  \href{https://mockinterviewerai.netlify.app/}{Live Demo}
  \,\textbar\,
  \href{https://drive.google.com/file/d/1p491yWfbeOLaWvnOIkI6u5gXdy28YbZl/view?usp=sharing}{Project Doc}
}
\begin{itemize}
  \resumeItem{Built a full-stack interview platform with voice-based interaction and automated response evaluation, real-time scoring, and analytics across role-specific question banks (Frontend, Backend, DSA, System Design, HR).}
  \resumeItem{Designed the backend with Express REST APIs and MongoDB; integrated LLM-driven adaptive question sequencing and communication analysis (filler-word detection, pacing).}
\end{itemize}

\vspace{4pt}

%--- Acadence
\noindent\textbf{\color{accent}Acadence --- Full-Stack E-Learning Platform}
\hfill \emph{React, Node.js, MongoDB, Google Gemini AI}\\
{\small
  \href{https://github.com/Ishita-coder27/acadence2.0}{GitHub}
  \,\textbar\,
  \href{https://acadence-dashboard-9b46.vercel.app}{Live Demo}
}
\begin{itemize}
  \resumeItem{Built a full-stack LMS with \textbf{JWT authentication}, gamification (streaks, badges, progress analytics), responsive dashboards, and AI-powered course generation via the Gemini API.}
  \resumeItem{Designed RESTful backend services and MongoDB schemas; enforced consistent structured (JSON) responses across the application.}
\end{itemize}

\vspace{4pt}

%--- Heallio
\noindent\textbf{\color{accent}Heallio --- Health Intelligence Platform}
\hfill \emph{React, FastAPI, PostgreSQL, Python}\\
{\small{Work in progress}}
\begin{itemize}
  \resumeItem{Built a full-stack health platform with \textbf{FastAPI + PostgreSQL}, designing a token-efficient data pipeline that reduced external API cost by $\sim$\textbf{60\%} and improved response latency.}
  \resumeItem{Implemented a modular extraction component (Regex + LLM fallback) with Pydantic-validated schemas and clean, reusable API interfaces.}
\end{itemize}

%================ EDUCATION ================
\section*{Education}

\resumeSubheading
{Jaypee Institute of Information Technology, Noida}{Jul 2023 -- Jun 2027}
{B.Tech in Computer Science \& Engineering}{GPA: 8.04 / 10}

%================ ACHIEVEMENTS ================
\section*{Achievements \& Certifications}

\begin{itemize}
  \resumeItem{Solved \textbf{500+ DSA problems} across graphs, dynamic programming, greedy, and hashing (LeetCode / Codeforces) --- strong algorithmic, problem-solving, and time-space optimization foundation.}
  \resumeItem{\textbf{Amazon ML Summer School 2025} \href{https://drive.google.com/file/d/1T9mSpv0DFmDpvxUingbAiahDqWr-zmf4/view?usp=sharing}{\small[Certificate]} --- Selected among top applicants nationwide for an advanced curriculum covering supervised/unsupervised learning, deep learning, and NLP.}
  \resumeItem{Consistent focus on \textbf{production-grade engineering}: modular architecture, clean REST API design, system-level thinking, and code quality across all projects and internships.}
\end{itemize}

\end{document}
